Scoring_questionnaires2021

### 2021-08-23 Questionnaires_scoring2021.Rmd
Update Questionnaires_scoring2021.Rmd

IAS: jvi8
working well om the app
https://xavierrg.shinyapps.io/datacleaning/
```{r}
library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/345_346_IAS_2021-08-21.csv")
View(db_IAS)

@@

BVAQ: 83b1
BPQ: bbc4

# Function that scores the Body Perception Questionnaire (BPQ) 
# (Cabrera et al., 2018) and all subscales
# Dependencies: 03_scoring_helpers.R, tidyverse

score_BPQ <- function(df){

  # Create a new temporary df to store the BPQ data 
  BPQ_data <- as_tibble(df) %>%
    select("Participant Private ID", 
           BAI_01:BAI_26, ANSR_01:ANSR_20, HHI_01:HHI_28) %>%
    # Recode factors into numerics
    mutate_at(.vars = vars(BAI_01:HHI_28), 
              .funs = recode(Never = 1, 
                             Mild = 2, 
                             Moderate = 3, 
                             Severe = 4, 
                             Debilitating = 5))

  print(BPQ_data)

  # Construct final scores
  BPQ_score <- tibble(
    "Participant Private ID" = BPQ_data$`Participant Private ID`,

    # Body awareness image
    BAI_score = sumvars(.df = BPQ_data, 
                        BAI_01:BAI_26) / 26,

    # Autonomic nervous system response
    ANSR_score = sumvars(.df = BPQ_data,
                         ANSR_01:ANSR_20) / 20,

    # Health history inventory
    HHI_score = sumvars(.df = BPQ_data,
                        HHI_01:HHI_28) / 28
  )

  return(BPQ_score)

}

>>>>

IAS: jvi8
working well om the app
https://xavierrg.shinyapps.io/datacleaning/
```{r eval=FALSE, include=FALSE}
library(readr)
db_IAS <- read_csv("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/IAS/345_346_IAS_2021-08-21.csv")
View(db_IAS)

@@

BPQ: bbc4

# Function that scores the Body Perception Questionnaire (BPQ) 
# (Cabrera et al., 2018) and all subscales
# Dependencies: 03_scoring_helpers.R, tidyverse
```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BPQ")

# read the files
read_selfrep <- function(flnm) {
    read_csv(flnm) %>%
        mutate(filename = flnm)
}

db_BPQ <- list.files(pattern = "*-bbc4.csv", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

# eliminate empty rows
db_BPQ<- subset(db_BPQ, db_BPQ$`Event Index`== 1)

db_BPQ$completion_code<- db_BPQ$`Participant Completion Code`

# store names for BPQ columns
bpq_names<- names(db_BPQ %>%

# score_BPQ <- function(df){
  # Create a new temporary df to store the BPQ data 
  # BPQ_data <- as_tibble(df) %>%
    select("Participant Private ID","completion_code", 
           BAI_01:BAI_26, ANSR_01:ANSR_20, HHI_01:HHI_28)%>%
  # drop anything with quantised or text
  select(-contains("text"))%>%
  select(-contains("quantised")))

bpq_names

# use the quantised columns as the response siunce they have a number rather than a string

db_BPQ1<- db_BPQ %>%

# score_BPQ <- function(df){
  # Create a new temporary df to store the BPQ data 
  # BPQ_data <- as_tibble(df) %>%
    select("Participant Private ID","completion_code", 
           BAI_01:`BAI_26-quantised`, ANSR_01:`ANSR_20-quantised`, HHI_01:`HHI_28-quantised`)%>%
  # drop anything with quantised or text
  # library(dplyr) 
  select(-contains("text")) %>%
  # select(-contains("quantised"))%>%

  # select the quantised to use as the coded variable
  select(c(1:2, contains("quantised")))

# score
# assign new names replacing quantised column names with BPQ only item names
names(db_BPQ1)<- bpq_names

colnames(db_BPQ1)
# do the actual scoring, only on the BPQ part - bpdy awareness
db_BPQ2<- db_BPQ1%>%
    # Recode factors into numerics
    # mutate_at(vars(BAI_01:HHI_28), 
    #           funs(car::recode("Never" = 1, 
    #                          "Occasionally" = 2, 
    #                          "Sometimes" = 3, 
    #                          "Usually" = 4, 
    #                          "Always" = 5)))
  select(c(1:28))%>%
   mutate(BPQ = rowSums(.[ 3:28]))

  #   # Autonomic nervous system response
  #   ANSR_score = sumvars(.df = BPQ_data,
  #                        ANSR_01:ANSR_20) / 20,
  #   
  #   # Health history inventory
  #   HHI_score = sumvars(.df = BPQ_data,
  #                       HHI_01:HHI_28) / 28
  # )
  #

db_BPQ2
db_BPQ3<- select(db_BPQ2, 1,2,29)
```

BVAQ: 83b1
https://www.psychologicabelgica.com/articles/10.5334/pb.302/print/
sum ramnge 40-200

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/BVAQ_83b1")
read_selfrep <- function(flnm) {
    readxl::read_xlsx(flnm) %>%
        mutate(filename = flnm)
}

db_BVAQ <- list.files(pattern = "*-83b1.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

# eliminate empty rows
db_BVAQ<- subset(db_BVAQ, db_BVAQ$`Event Index`== 1)

db_BVAQ$completion_code<- db_BVAQ$`Participant Completion Code`

View(db_BVAQ)

db_BVAQ1<- db_BVAQ %>%
   select( -contains("quantised"))%>%
   select(c("Participant Private ID","completion_code",BVAQ_01:BVAQ_40))

db_BVAQ1<- db_BVAQ1%>%
   mutate(BVAQ = rowSums(.[ 3:42]))

db_BVAQ3<- select(db_BVAQ1, c(1,2,43))
```

demographics
8zto- age
8nsp - vision
v2gn = mental health

```{r}
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/selfreport/Short format/Demographics_8zto_8nsp_v2gn")

db_age <- list.files(pattern = "*-8zto.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

db_vision <- list.files(pattern = "*-8nsp.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))
db_mhealth <- list.files(pattern = "*-v2gn.xlsx", 
               full.names = T) %>% 
    map_df(~read_selfrep(.))

colnames(db_mhealth)
# db_mhealth<- subset(db_mhealth, -2:12,14:15,17:26)

bind (db_mhealth, db_vision, db_age, by = `Participant Private ID`)

colnames(db_age)
db_age$age_response_specific
db_age$gender_response
db_age$`gender_response-quantised`
# db_age$`AgeResponse-text`
db_age1<- select(db_age, c(1,13,16,36,37,41))

colnames(db_mhealth)

db_mhealth$ASD
db_mhealth$`ASD-text`
db_mhealth$clinical_diagnosis
db_mhealth$mental_health
db_mhealth$`mental_health-text`
db_mhealth$medication
db_mhealth1<- select(db_mhealth, c(1,13,16, 33,34,37:38,40))

colnames(db_vision)
db_vision$EyesightResponse
db_vision1<- select(db_vision, c(1,13,16, 33,34,36:37))

db_demog<- left_join(db_vision1, db_mhealth1,db_age1, by = c("Participant Private ID",
                                                   "Participant Completion Code"))%>%
  subset(!is.na(`Participant Private ID`))

db_demog$completion_code <- db_demog$`Participant Completion Code`

IQ
IQ: esh8
```{r}
IQ: esh8
